Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-03 PAPER.tex
Finished paragraph on how negative correlation arises.  May still want to add an appendix with explicit math.

However, a deeper investigation of these cross-terms reveals that they can contain non-negligible power when $\textbf{R}_{r}$
is taken to be $\textbf{C}_{r}^{-1}$ and
$\textbf{C}_{r}$ is estimated from the data itself.  As shown in \citet{switzer_et_al2015}, 
$\textbf{C}_{r}^{-1}\textbf{x}$ and
$\textbf{C}_{r}^{-1}\textbf{e}$
become anti-correlated on average. This negative cross-term power arises from inverting the covariance matrix
$\textbf{C}_{r}$. Mathematically, the covariance of the data plus EoR is:

@@

\noindent and we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
The middle 
two terms, however, can have power in their off-diagonal terms.  As shown in Appendix C of \citet{parsons_et_al2014}, the
inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms.
\cc{someone help me write this more elegantly... (not done yet)}

The spurious correlation between $\textbf{e}$ and $\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

>>>>

However, a deeper investigation of these cross-terms reveals that they can contain non-negligible power when $\textbf{R}_{r}$
is taken to be $\textbf{C}_{r}^{-1}$ and
$\textbf{C}_{r}$ is estimated from the data itself.  As shown in \citet{switzer_et_al2015}, 
$\textbf{C}_{r}^{-1}\textbf{x}$ and
$\textbf{C}_{r}^{-1}\textbf{e}$
can become anti-correlated on average. 
This negative cross-term power arises from inverting the covariance matrix
$\textbf{C}_{r}$. 
Intuitively, we can see this by expanding the covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
$|\textbf{x}|\ll|\textbf{e}|$ regime:

@@

\noindent and we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
The middle 
two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
ensemble, $\langle\textbf{xe}^\dagger\rangle$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, the
inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}$ is multiplied into $\textbf{x}$,
the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}$), but
contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\textbf{C}^{-1}$. The
correlation is negative because the product $\textbf{C}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
of the off-diagonal terms in $\textbf{C}^{-1}$ while retaining the negative sign that arose from the inversion
of a diagonal-dominant matrix.
% XXX [ARP: we may want to write this all out explicitly in an appendix]

The spurious correlation between $\textbf{C}_r^{-1}\textbf{e}$ and $\textbf{C}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
